Data_Setup

### 2020-07-29 R/Plots_manuscript_v0.3.Rmd

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "FL50" ~ "50% flowering",
                              phe == "dyln_fl50" ~ "daylength",
                              phe == "dyln_change_sec" ~ "daylength change (s)",
                              phe == "cgdd_12c_gr2fl" ~ "GDD, GR to FL",
                              phe == "crain_gr2fl" ~ "Rainfall, GR to FL",
                              phe == "crain_1d" ~ "Rainfall, 1 day",
                              phe == "crain_2d" ~ "Rainfall, 2d sum",
                              phe == "crain_3d" ~ "Rainfall, 3d sum",
                              phe == "crain_5d" ~ "Rainfall, 5d sum",
                              phe == "crain_7d" ~ "Rainfall, 7d sum",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "nine_sites"))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% flowering", "daylength",
                                                  "daylength change (s)",
                                                  "GDD, GR to FL",
                                                  "Rainfall, GR to FL",
                                                  "Rainfall, 1 day",
                                                  "Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum",
                                                  "Rainfall, 7d sum"
                                                  ))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
site_plot <- c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD", "All", "Texas", "North")

flh2_p1 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)

save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_v2.png", plot = flh2_p1, base_height = 7, base_asp = 1.3)

@@

flh2_p2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

@@

```{r}
unique(h2gr$site)
grh2 <- h2gr %>%
  filter(!(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d", "DYLN"))) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "All",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              phe == "cgdd_12c_jan2gr" ~ "GDD 01-01 to greenup",
                              phe == "cgdd_8c_jan2gr" ~ "GDD 8C 01-01 to greenup",
                              phe == "tmax_18d" ~ "Max T, 18d mean",
                              phe == "tmin_18d" ~ "Min T, 18d mean",
                              phe == "tave_18d" ~ "Mean T, 18d mean",
                              phe == "tmax_10d" ~ "Max T, 10d mean",
                              phe == "tmin_10d" ~ "Min T, 10d mean",
                              phe == "tave_10d" ~ "Mean T, 10d mean",
                              phe == "tmax_5d" ~ "Max T, 5d mean",
                              phe == "tmin_5d" ~ "Min T, 5d mean",
                              phe == "tave_5d" ~ "Mean T, 5d mean",
                              phe == "cgdd_12c_10d" ~ "GDD, 10d",
                              phe == "cgdd_12c_18d" ~ "GDD, 18d",
                              phe == "cgdd_12c_5d" ~ "GDD, 5d",
                              TRUE ~ phe))
grh2$site <- factor(grh2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North", "nine_sites"))
grh2$phe_name <- factor(grh2$phe_name, levels = c("50% greenup", "GDD, 5d",
                                                  "Min T, 5d mean",
                                                  "Mean T, 5d mean",
                                                  "Max T, 5d mean",
                                                  "GDD, 10d",
                                                  "Min T, 10d mean",
                                                  "Mean T, 10d mean",
                                                  "Max T, 10d mean",
                                                  "GDD, 18d",
                                                  "Min T, 18d mean",
                                                  "Mean T, 18d mean",
                                                  "Max T, 18d mean",
                                                  "GDD 8C 01-01 to greenup",
                                                  "GDD 01-01 to greenup"))
grh2$subpop_name <- factor(grh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "All"))

@@

grh2_p1 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v2.png", plot = grh2_p1, base_height = 7, base_asp = 1.3)

@@

grh2_p2 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v3.png", plot = grh2_p2, base_height = 5, base_asp = 1.5)

@@

grh2_p3 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.15)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v4.png", plot = grh2_p3, base_height = 4, base_asp = 1.5)

gr_fl_p1 <- plot_grid(grh2_p3, flh2_p2, nrow = 2)
```
## Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

@@

      }
    }
  }
  write_csv(h2_table, file.path(outputdir, paste0("h2_df_", phe_v[1],
                                                  "_related_functions_", 
                                                  "of_weather_v4.csv")))
}

>>>>

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "FL50" ~ "50% flowering",
                              phe == "dyln_fl50" ~ "daylength",
                              phe == "dyln_change_sec" ~ "daylength change (s)",
                              phe == "cgdd_12c_gr2fl" ~ "GDD, GR to FL",
                              phe == "crain_gr2fl" ~ "Rainfall, GR to FL",
                              phe == "crain_1d" ~ "Rainfall, 1 day",
                              phe == "crain_2d" ~ "Rainfall, 2d sum",
                              phe == "crain_3d" ~ "Rainfall, 3d sum",
                              phe == "crain_5d" ~ "Rainfall, 5d sum",
                              phe == "crain_7d" ~ "Rainfall, 7d sum",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "nine_sites")))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% flowering", "daylength",
                                                  "daylength change (s)",
                                                  "GDD, GR to FL",
                                                  "Rainfall, GR to FL",
                                                  "Rainfall, 1 day",
                                                  #"Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum"#,
                                                  #"Rainfall, 7d sum"
                                                  ))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
site_plot <- rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD", "All", "Texas", "North"))
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))

flh2_p1 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)

save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_v3.png", plot = flh2_p1, base_height = 7, base_asp = 1.1)

@@

flh2_p2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.45)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

@@

```{r}
unique(h2gr$site)
grh2 <- h2gr %>%
  filter(!(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d", "DYLN"))) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "All",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              phe == "cgdd_12c_jan2gr" ~ "GDD 01-01 to GR",
                              phe == "cgdd_8c_jan2gr" ~ "GDD 8C 01-01 to greenup",
                              phe == "tmax_18d" ~ "Max T, 18d mean",
                              phe == "tmin_18d" ~ "Min T, 18d mean",
                              phe == "tave_18d" ~ "Mean T, 18d mean",
                              phe == "tmax_10d" ~ "Max T, 10d mean",
                              phe == "tmin_10d" ~ "Min T, 10d mean",
                              phe == "tave_10d" ~ "Mean T, 10d mean",
                              phe == "tmax_5d" ~ "Max T, 5d mean",
                              phe == "tmin_5d" ~ "Min T, 5d mean",
                              phe == "tave_5d" ~ "Mean T, 5d mean",
                              phe == "cgdd_12c_10d" ~ "GDD, 10d",
                              phe == "cgdd_12c_18d" ~ "GDD, 18d",
                              phe == "cgdd_12c_5d" ~ "GDD, 5d",
                              TRUE ~ phe))
grh2$site <- factor(grh2$site, levels = rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North", "nine_sites")))
grh2$phe_name <- factor(grh2$phe_name, levels = c("50% greenup", "GDD, 5d",
                                                  "Min T, 5d mean",
                                                  #"Mean T, 5d mean",
                                                  #"Max T, 5d mean",
                                                  "GDD, 10d",
                                                  "Min T, 10d mean",
                                                  #"Mean T, 10d mean",
                                                  #"Max T, 10d mean",
                                                  "GDD, 18d",
                                                  "Min T, 18d mean",
                                                  #"Mean T, 18d mean",
                                                  #"Max T, 18d mean",
                                                  #"GDD 8C 01-01 to greenup",
                                                  "GDD 01-01 to GR"))
grh2$subpop_name <- factor(grh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "All"))

@@

grh2_p1 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v2.png", plot = grh2_p1, base_height = 7.5, base_asp = 1.1)

@@

grh2_p2 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v3.png", plot = grh2_p2, base_height = 5, base_asp = 1.3)

@@

grh2_p3 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.11)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_v4.png", plot = grh2_p3, base_height = 4, base_asp = 1.5)

gr_fl_p1 <- plot_grid(grh2_p3, flh2_p2, nrow = 2)

save_plot("../manuscript/plots/h2_GR_and_FL_site_weather_functions_All_Sites.png", plot = gr_fl_p1, base_height = 4.6, base_asp = 1.35)
```
## Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

@@

      }
    }
  }
  write_csv(h2_table, file.path(outputdir, paste0("h2_df_", phe_v[1],
                                                  "_related_functions_", 
                                                  "of_weather_v4.csv")))
}
```

# D2F

If flowering date frequently varies as a function of GDD in switchgrass, this explains observations that moving southern populations northwards delays flowering, and moving northern populations south hastens flowering (Sanderson et al 1996). < Indeed, we observed D2F for Midwest plants was shorter at TX than BRKG, and vice versa?>

```{r}
d2f_lat <- phenotypes %>%
  mutate(D2F = FL50 - GR50) %>%
  left_join(select(metadata, PLANT_ID, SUBPOP)) %>%
  filter(!(SITE %in% c("OVTN", "FRMI")) & WHERE == "GWAS" & SUBPOP %in% c("Gulf", "Midwest")) %>%
  group_by(SUBPOP, SITE) %>%
  summarise(mean_D2F = mean(D2F, na.rm = TRUE)) %>%
  left_join(select(sites, SITE, Latitude, manu_site)) %>%
  arrange(SUBPOP, Latitude) 
d2f_lat %>%
  ggplot(aes(x = Latitude, y = mean_D2F)) +
  geom_point(aes(color = SUBPOP))

summary(lm(mean_D2F ~ Latitude*SUBPOP, data = d2f_lat))
82-55
```

## G_BLUP GWAS

```{r}
gwasdir <- file.path(workingdir, "analysis", "gwas", "G_BLUP")
log10p_gulf <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Gulf.rds"))
log10p_midw <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Midwest.rds"))
log10p_gandm <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Gulf_and_Midwest.rds"))
```

```{r}
log10p_gulf %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/10300000)) %>%
  group_by(PHE) %>%
  tally() %>%
  write_csv(., "../manuscript/tables/Gulf_SNPs_above_Bonferroni_by_trait.csv")
```

```{r}
log10p_midw %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/8800000)) %>%
  group_by(PHE) %>%
  tally() %>%
  write_csv(., "../manuscript/tables/Midwest_SNPs_above_Bonferroni_by_trait.csv")

log10p_gandm %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/12100000)) %>%
  group_by(PHE) %>%
  tally() %>%
  write_csv(., "../manuscript/tables/Gulf_and_Midwest_diversity_panel_SNPs_above_Bonferroni_by_trait.csv")
```

```{r}
gulf_top <- readRDS(file.path(gwasdir, "Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Gulf.rds"))

gulf_top %>%
  group_by(n_cond_in_top_set) %>%
  tally()
```

### 2020-07-29 data-raw/Data_Setup.Rmd

fwy_prev <- fwy_prev_raw %>%
  separate(ENVI, into = c("SITE", "YEAR"), sep = "_") %>%
  group_by(LINE, SITE, YEAR) %>%
  mutate(PLOT_GL = paste0(str_sub(SITE, end = 1), str_sub(YEAR, start =3, end = 4), "_", row_number())) %>%
  mutate(YEAR = as.numeric(YEAR),
         WHERE = "FWCR") %>%
  pivot_longer(cols = BIOMASS:HT, names_to = "PHE", values_to = "MEAS") %>%
  rename(PLANT_ID = LINE) %>%
  filter(PHE %in% c("FL50", "GR50"))
fwy_2019 <- fourway %>%
  separate(ENVI, into = c("SITE", "YEAR"), sep = "_") %>%
  group_by(LINE, SITE, YEAR) %>%
  mutate(PLOT_GL = paste0(str_sub(SITE, end = 1), str_sub(YEAR, start =3, end = 4), "_", row_number())) %>%
  mutate(YEAR = as.numeric(YEAR),
         WHERE = "FWCR") %>%
  pivot_longer(cols = FL50:HT, names_to = "PHE", values_to = "MEAS") %>%
  rename(PLANT_ID = LINE) %>%
  filter(PHE %in% c("FL50", "GR50"))

@@

phe_all %>%
  group_by(PLOT_GL, SITE, PLANT_ID, YEAR) %>%
  tally() %>% arrange((n))

@@

cgdd_df <- wea_gr_fl2 %>%
  group_by(SITE, PLANT_ID, PLOT_GL, GR50, FL50) %>%
  summarise(CGDD_12C = sum(GDD_12C_SM),
            PTT_12C = sum(PTT_12C),
            CRAIN = sum(RAIN_SM)
            )

@@

wea_gr_fl3 <- wea_gr_fl %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(between(Day_of_year, FL50-5, FL50)) %>% 
  ungroup() 
crain_df <- wea_gr_fl3 %>%
  group_by(SITE, PLANT_ID, PLOT_GL, GR50, FL50) %>%
  summarise(CGDD_12C_5d = sum(GDD_12C_SM),
            PTT_12C_5d = sum(PTT_12C),
            CRAIN_5d = sum(RAIN_SM)
            )
wea_gr_fl4 <- wea_gr_fl %>%
  ungroup() %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(Day_of_year == FL50) %>% 
  rename(dyln_fl50 = DYLN) %>%
  dplyr::select(-(TMAX:Day_of_year), -(TMAX_SM:PTT_12C))

@@

write_rds(cumweadf, path = "../data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
```
### -------

>>>>

fwy_prev <- fwy_prev_raw %>%
  separate(ENVI, into = c("SITE", "YEAR"), sep = "_") %>%
  group_by(LINE, SITE, YEAR) %>%
  mutate(PLOT_GL = paste0(str_sub(SITE, end = 1), str_sub(YEAR, start =3, end = 4), "_", row_number())) %>%
  mutate(YEAR = as.numeric(YEAR),
         WHERE = "FWCR") %>%
  pivot_longer(cols = BIOMASS:HT, names_to = "PHE", values_to = "MEAS") %>%
  rename(PLANT_ID = LINE) %>%
  filter(PHE %in% c("FL50", "GR50"))
fwy_2019 <- fourway %>%
  separate(ENVI, into = c("SITE", "YEAR"), sep = "_") %>%
  group_by(LINE, SITE, YEAR) %>%
  mutate(PLOT_GL = paste0(str_sub(SITE, end = 1), str_sub(YEAR, start = 3, 
                                                          end = 4), "_", row_number())) %>%
  mutate(YEAR = as.numeric(YEAR),
         WHERE = "FWCR") %>%
  pivot_longer(cols = FL50:HT, names_to = "PHE", values_to = "MEAS") %>%
  rename(PLANT_ID = LINE) %>%
  filter(PHE %in% c("FL50", "GR50"))

@@

phe_all %>%
  group_by(WHERE) %>%
  tally() %>% arrange((n))

@@

cgdd_df <- wea_gr_fl2 %>%
  group_by(WHERE, SITE, PLANT_ID, PLOT_GL, GR50, FL50) %>%
  summarise(CGDD_12C = sum(GDD_12C_SM),
            PTT_12C = sum(PTT_12C),
            CRAIN = sum(RAIN_SM)
            )

@@

wea_gr_fl3 <- wea_gr_fl %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(between(Day_of_year, FL50-5, FL50)) %>% 
  ungroup()

cumweadf %>%
  group_by(WHERE) %>%
  tally() %>% arrange((n))

crain_df <- wea_gr_fl3 %>%
  group_by(WHERE, SITE, PLANT_ID, PLOT_GL, GR50, FL50) %>%
  summarise(CGDD_12C_5d = sum(GDD_12C_SM),
            PTT_12C_5d = sum(PTT_12C),
            CRAIN_5d = sum(RAIN_SM)
            )
wea_gr_fl4 <- wea_gr_fl %>%
  ungroup() %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(Day_of_year == FL50) %>% 
  rename(dyln_fl50 = DYLN) %>%
  dplyr::select(-(TMAX:Day_of_year), -(TMAX_SM:PTT_12C))

@@

write_rds(cumweadf, path = "../data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
```

```{r}
fourway = cumweadf[cumweadf$WHERE == "FWCR",]
df
fourway
```

### -------
